\documentclass[9pt,letterpaper]{article}
\usepackage{setspace}
\doublespacing
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[margin=1.0in]{geometry}
\usepackage{ifpdf}
\makeatletter
\@namedef{ver@thumbpdf.sty}{}
\makeatother
\author{}
\date{}
\title{\vspace{-3.5cm} Sabon is an ass - By Matthew "Vyajr" Ramirez\vspace{-2.5cm}}
\begin{document}
\maketitle
\vspace{1.0cm}
Yesterday I was informed that Sabon (will be referred to as Back Stabbon or Stabbon for short) is denying my ability to receive a Felsteel Annihilator (Mount) from the raid in general as he has claimed to have say I have contributed nothing to the raid. This may be news to some of you as this was quite a shocking thing to hear for me. Followed by a string of surreal statements from Stabbon, I have come to the conclusion that he is determined to make sure I don't receive a mount. So I have decided to write this to help everyone understand the situation and why Stabbon is an ass.\vspace{0.5cm}

First we must talk about what he means by the statement in which he stated I have contributed nothing to the raid. What does contributing mean? Based on the definition it is "the part played by a person or thing in bringing about a result or helping something to advance". So we can infer that over and claim that it is a person who helped advance the raid in some regards. Using that definition we can apply it immediately as the 5 kills I have for mythic Hellfire Citadel, which are in fact my only 5 kills were only due to the fact that I had to step in for the raid on those times to provide a spot to allow the raid to progress or there would have been no raid that day as there was a missing player. When Stabbon or Mallard asked me to join to help them (the raid), I unequivocally said yes and joined the raid. While you can argue that 4 of them were not progression bosses, so I didn't provide much than a "body", 1 of them was a progression fight, that I downed with the main raid. In this case I could argue that I contributed something, successful progression help on 1 boss and keeping the raid from getting someone else most likely worse than me to replace the 20th player for the clearing of those other 4 bosses (which at the time weren't the speed runs they are now). Now that might seem like a lot, but then you have to see what others have done to compare it to.\vspace{0.5cm}

To compare me to the other raiders who are apart of the main raid, there is no argument here and I don't believe I have contributed as much or nearly close to any of them so I will not be implying nor arguing for saying I am on the same level. What I will argue for is the "bench/new recruits" that have been added recently. Again we will look at them with an unbiased look at "contribution" to the raid they have provided. Based on what I can tell, there has been an addition of the new DK, Touch, Monk Grill to the raid. Now to the capacity I can tell, they have been added to the raid for nothing more than just farm. They were not apart of any progression bosses and provide a "body" for the fights. So based on progression bosses done, I have them beat, 1/13 beats 0/13 for progression (albeit Council may have been easy now compared to later bosses, but it wasn't at the time). So we can look at farm, while they probably have me beat on that, they were at least brought to farm, after countless efforts to join the first 5 bosses of mythic farm when it was being offered, I was denied by Stabbon as you could have guessed. So I cannot compete with them in farm. But if they weren't there, the raid would still go on, compared to when I was invited, I was providing the body that was \underline{needed} for the raid to progress for the night. Now the last argument that could be made is that the benched players who were added, know the fights and have the gear, which both I cannot compete with. But as many of you know I could probably learn the boss within a pull as many of you know who have raided with me before I may be an asshole but I could play decently mechanically. As someone once said, "I want you guys to be jrs", as for gear with Stabon denying me to attend the farm bosses (just the first 5) could have netted me some better gear and allowed me to get the mythic cache.\vspace{0.5cm}

So we are left with the only argument left, which is maybe there is a hatred against me and many simply would just not like to have me have the mount. Now there is no argument to say you are wrong because it is your opinion and that cannot change but we must be unbiased in this decision. I am not asking to receive the mount now, I am simply asking that I should be added to the list as I have technically contributed, again as I state not as much as others but clearly there is something there to argue for. Now Stabbon would like to claim that I am asking for handouts such as I have done nothing for the progression of this raid tier and I am simply asking for the mount with no ground to support this claim. While maybe some of you might see this argument as valid, you have to remember in the prepatch right before Warlords was out, Stabbon received all of the gear + boa from the raid for free. He was brought to the raid and received all of the benefits without even logging on during the Mists of Pandaria expansion once besides the last week before Warlords was dropped. This could definitely be considered receiving handouts, where he provided nothing to the raid. I was told to pay 80k to receive this same benefit, as well as Desit who paid some amount which I cannot recall. Stabbon claims that he did not ask for this handout and was given to him with no persuasion or inquiring about it. I am simply asking for the mount \underline{eventually}, where I can at least argue I provided something, more so than Stabbon provided to the raid when he did receive the boa.\vspace{0.5cm}

Based on the evidence or information I have provided I implore you, officers of the guild, to override Stabbon executive order in which he as issued upon me and to allow me to be in the listing to receive the mount. I think I have been able to provide a contribution to the raid more-so than the 3 that I talked about (which I don't say they cannot receive one as well, but more-so if they are allowed to, so should I) or at least equal to their effort. I was always more than happy to help out the raid in those 5 times and on some other bosses I did kill in which I came and installed addons which I never used to help kill the boss or at times where I was invited to help clear only to be told that I needed to leave 10 minutes after as the person who I needed to replace actually attended the raid. I would like the Felsteel Annihilator and I beleive the only person stopping me from having a shot at it is Stabbon. If this has not convinced you to let me at least be on the list to receive one, I would like to be notified immediately as I would just purchase it from another guild instead and it will give me ample time to find the guild and gold for it. 

TL;DR - Sabon is an ass
\end{document}